---
title: "R Notebook -- Predicting prices in a housing dataset"
output: html_notebook
---

```{r}
library(readr)

data <- read_csv('Housing.csv')
head(data)

```

```{r}
library(dplyr)
library(rsample)
library(ggplot2)
library(corrr)
library(recipes)
library(parsnip)
library(broom)

housing <- data

housing %>% 
  select(where(~ !is.factor(.x))) %>% 
  corrr::correlate() %>% 
  corrr::focus(price) %>%
  corrr::fashion()
```

```{r}
library(dplyr)
library(rsample)
library(ggplot2)
library(corrr)
library(recipes)
library(parsnip)

housing %>% 
  select(where(~ !is.factor(.x))) %>% 
  corrr::correlate() %>% 
  corrr::focus(price) %>% 
  filter(price > 0.4) %>% 
  pull(term) -> high_corr_vars  #returns area and bathrooms / stories as highest correlated variables
 
```
```{r}

housing %>% 
  select(where(~ !is.factor(.x))) %>% 
  corrr::correlate() %>% 
  #corrr::fashion() %>% 
  corrr::network_plot()

```



```{r}
library(dplyr)
housing <- data

housing %>% 
  select(high_corr_vars, price) -> housing

housing
```

Split Data
```{r}
library(rsample)

housing_split <- initial_split(housing, strata = price)
training_data <- training(housing_split)
testing_data  <- testing(housing_split)


``` 

DATA PREPROCESSING
```{r}
#training_data %>% 
  recipe(price ~., training_data) %>% 
  step_dummy(all_nominal()) %>% 
  step_normalize(all_numeric(), -all_outcomes()) %>% 
  prep() -> the_recipe

juice(the_recipe) -> juiced
```

********
Use Parsnip to apply regression type, linear reg in this case
```{r}
lm_model <- parsnip::linear_reg() %>% 
  set_engine("lm") %>% 
  set_mode("regression")
```


MODEL FITTING -- Fit model on the juiced recipe
```{r}
lm_fit <- fit(lm_model, price ~., juiced)
lm_fit
```
PREDICTIONS -- Pipe the lm_fit into the predict fxn
```{r}

lm_fit %>% 
  predict(new_data = juiced) %>% 
  mutate(truth = training_data$price) -> predicts_train

lm_fit %>% 
  predict(new_data = bake(the_recipe, testing_data)) %>% 
  mutate(truth = testing_data$price) -> predicts_test

```

```{r}
predicts_train %>% 
  mutate(type = "train") %>% 
  bind_rows(
    predicts_test %>% 
      mutate(type = 'test')
    ) -> results
```

ACCURACY TEST -- Using yardstick
```{r}
library(yardstick)
results %>% 
  group_by(type) %>% 
  yardstick::rmse(truth, .pred)
```
Difference in Estimates not wide, thus model is generalizing well.

# Plotting true prices vs predictions
```{r}
library(dplyr)
library(ggplot2)
library(plotly)

results %>% 
  group_by(type) %>% 
  ggplot(aes(x = truth, y = .pred)) +
  geom_point() +
  geom_abline(col = 'red', size = 3) +
  theme_bw() +
  labs(
    x = 'Actual housing Prices',
    y = 'Predicted Prices'
  )
                

```

# Now to predictions on new, fresh data

```{r}
#Create fresh, unseen data
tibble(
  area = c(7450,12001,6877,9960,16200,14200),
  bathrooms = c(4,5,1,2,5,6),
  stories = c(2,3,2,3,3,2)
  ) -> new_houses

#preprocess the new data and juice
new_houses %>%  #data to pipe into the recipe
  recipe() %>%  #starts with recipe
    step_normalize(everything()) %>%  #normalize then preprocess
  prep() -> recipe #ends with prep

  juice(recipe) -> juiced_new #don't forget to juice the recipe
```

Use model to predict fresh, new data
```{r}
library(dplyr)

predict(lm_fit, new_data = juiced_new) -> predictions
predictions

new_houses %>% 
  mutate(price = predictions$.pred + 4761314) -> new_houses

new_houses
```


